### 2017-01-26 presentation/benchmarks.tex
copied all the relevant content from the paper to the presentation

\section{Benchmarks}
To check the performance of our new parallel arrow API, we conducted some benchmarks. These are based on a sudoku solver from the examples for Simon Marlows book "Parallel and Concurrent Programming in Haskell" which can be found on his GitHub \cite{marlow_parconc}. The results are displayed in the following graphs which are ordered by problem size.
\\\\
The Benchmarks were run on a Core i7-3970X CPU @ 3.5GHz with 6 cores and 12 threads. For sake of comparability with Simon Marlow's parallel version which uses the ParMonad, we use the ParMonad backend for the parallel arrow versions as well.
\\\\
\framebox{
	\begin{tikzpicture}[thick, scale=0.7]
	\begin{axis}[
	xbar, xmin=0,
	width=12cm, height=7cm, enlarge y limits=0.5,
	xlabel={avg. seconds run on sudoku17.1000.txt (100 runs)},
	symbolic y coords={parrows-sudoku-farmChunk, parrows-sudoku-farm, parrows-sudoku-parmapstream, parrows-sudoku-parmap, parmonad-sudoku-parmap, sudoku-sequential},
	ytick=data,
	nodes near coords, nodes near coords align={horizontal},
	]
	\addplot coordinates {(.215,parrows-sudoku-farmChunk) (.213,parrows-sudoku-farm) (.188,parrows-sudoku-parmapstream) (.197,parrows-sudoku-parmap) (.527,parmonad-sudoku-parmap) (1.338,sudoku-sequential)};
	\end{axis}
	\end{tikzpicture}
}
\\\\
\textit{Note: the bad result for parmonad-sudoku-parmap seems to be a artefact as it performs much better in the other benchmarks}
\\\\
\framebox{
	\begin{tikzpicture}[thick, scale=0.7]
	\begin{axis}[
	xbar, xmin=0,
	width=12cm, height=7cm, enlarge y limits=0.5,
	xlabel={avg. seconds run on sudoku17.16000.txt (100 runs)},
	symbolic y coords={parrows-sudoku-farmChunk, parrows-sudoku-farm, parrows-sudoku-parmapstream, parrows-sudoku-parmap, parmonad-sudoku-parmap, sudoku-sequential},
	ytick=data,
	nodes near coords, nodes near coords align={horizontal},
	]
	\addplot coordinates {(3.218,parrows-sudoku-farmChunk) (3.148,parrows-sudoku-farm) (2.755,parrows-sudoku-parmapstream) (2.860,parrows-sudoku-parmap) (2.936,parmonad-sudoku-parmap) (21.324,sudoku-sequential)};
	\end{axis}
	\end{tikzpicture}
}
\\\\
\framebox{
	\begin{tikzpicture}[thick, scale=0.7]
	\begin{axis}[
	xbar, xmin=0,
	width=12cm, height=7cm, enlarge y limits=0.5,
	xlabel={avg. seconds run on sudoku17.49151.txt (100 runs)},
	symbolic y coords={parrows-sudoku-farmChunk, parrows-sudoku-farm, parrows-sudoku-parmapstream, parrows-sudoku-parmap, parmonad-sudoku-parmap, sudoku-sequential},
	ytick=data,
	nodes near coords, nodes near coords align={horizontal},
	]
	\addplot coordinates {(10.038,parrows-sudoku-farmChunk) (10.151,parrows-sudoku-farm) (8.776,parrows-sudoku-parmapstream) (8.969,parrows-sudoku-parmap) (8.679,parmonad-sudoku-parmap) (60.931,sudoku-sequential)};
	\end{axis}
	\end{tikzpicture}
}
\\\\
As we can see, the parallel arrow versions of the program all have around the same speedup as the ParMonad based version. This means that using the \code{ArrowParallel} typeclass doesn't add any real notable overhead. Also, the slightly worse results for "parrows-sudoku-farm" and "parrows-sudoku-farmChunk" can be explained by either imperfect parameters or by the fact that the benchmarks do not really require the scheduling introduced by the skeletons which in this case introduces unnecessary overhead. This would probably look different if the benchmark would use e.g. a divide and conquer approach to solve the sudoku puzzles.

>>>>

\section{Benchmarks}
The Benchmarks were run on a Core i7-3970X CPU @ 3.5GHz with 6 cores and 12 threads. For sake of comparability with Simon Marlow's parallel version which uses the ParMonad, we use the ParMonad backend for the parallel arrow versions as well.
\frbreak
\framebox{
	\begin{tikzpicture}[thick, scale=0.7]
	\begin{axis}[
	xbar, xmin=0,
	width=12cm, height=7cm, enlarge y limits=0.5,
	xlabel={avg. seconds run on sudoku17.1000.txt (100 runs)},
	symbolic y coords={parrows-sudoku-farmChunk, parrows-sudoku-farm, parrows-sudoku-parmapstream, parrows-sudoku-parmap, parmonad-sudoku-parmap, sudoku-sequential},
	ytick=data,
	nodes near coords, nodes near coords align={horizontal},
	]
	\addplot coordinates {(.215,parrows-sudoku-farmChunk) (.213,parrows-sudoku-farm) (.188,parrows-sudoku-parmapstream) (.197,parrows-sudoku-parmap) (.527,parmonad-sudoku-parmap) (1.338,sudoku-sequential)};
	\end{axis}
	\end{tikzpicture}
}
\frbreak
\framebox{
	\begin{tikzpicture}[thick, scale=0.7]
	\begin{axis}[
	xbar, xmin=0,
	width=12cm, height=7cm, enlarge y limits=0.5,
	xlabel={avg. seconds run on sudoku17.16000.txt (100 runs)},
	symbolic y coords={parrows-sudoku-farmChunk, parrows-sudoku-farm, parrows-sudoku-parmapstream, parrows-sudoku-parmap, parmonad-sudoku-parmap, sudoku-sequential},
	ytick=data,
	nodes near coords, nodes near coords align={horizontal},
	]
	\addplot coordinates {(3.218,parrows-sudoku-farmChunk) (3.148,parrows-sudoku-farm) (2.755,parrows-sudoku-parmapstream) (2.860,parrows-sudoku-parmap) (2.936,parmonad-sudoku-parmap) (21.324,sudoku-sequential)};
	\end{axis}
	\end{tikzpicture}
}
\frbreak
\framebox{
	\begin{tikzpicture}[thick, scale=0.7]
	\begin{axis}[
	xbar, xmin=0,
	width=12cm, height=7cm, enlarge y limits=0.5,
	xlabel={avg. seconds run on sudoku17.49151.txt (100 runs)},
	symbolic y coords={parrows-sudoku-farmChunk, parrows-sudoku-farm, parrows-sudoku-parmapstream, parrows-sudoku-parmap, parmonad-sudoku-parmap, sudoku-sequential},
	ytick=data,
	nodes near coords, nodes near coords align={horizontal},
	]
	\addplot coordinates {(10.038,parrows-sudoku-farmChunk) (10.151,parrows-sudoku-farm) (8.776,parrows-sudoku-parmapstream) (8.969,parrows-sudoku-parmap) (8.679,parmonad-sudoku-parmap) (60.931,sudoku-sequential)};
	\end{axis}
	\end{tikzpicture}
}

### 2017-01-26 presentation/parrows.tex
copied all the relevant content from the paper to the presentation

\section{Parallel Arrows}
We have seen what Arrows are and how they can be used as a general interface to computation. In the following section we will discuss how Arrows can also be looked at as a general interface not only to computation, but to \textbf{parallel computation} as well. We start by introducing the interface and explaining the reasonings behind it. Then, we discuss some implementations using exisiting parallel Haskells. Finally, we explain why using Arrows for expressing parallelism is beneficial.
\subsection{The ArrowParallel typeclass}
As we have seen earlier, in its purest form, parallel computation (on functions) can be looked at as the execution of some functions \code{a -> b} in parallel:
\begin{lstlisting}[frame=htrbl]
parEvalN :: [a -> b] -> [a] -> [b]
\end{lstlisting}
Translating this into arrow terms gives us a new operator \code{parEvalN} that lifts a list of arrows \code{[arr a b]} to a parallel arrow \code{arr [a] [b]} (This combinator is similar to our utility function listApp, but does parallel instead of serial evaluation).
\begin{lstlisting}[frame=htrbl]
parEvalN :: (Arrow arr) => [arr a b] -> arr [a] [b]
\end{lstlisting}
With this definition of \code{parEvalN}, parallel execution can be looked at as yet another arrow combinator. But as the implementation may differ depending on the actual type of the arrow \code{arr} and we want this to be an interface for different backends, we have to introduce the new typeclass \code{ArrowParallel} to host this combinator.
\begin{lstlisting}[frame=htrbl]
class Arrow arr => ArrowParallel arr a b where
	parEvalN :: [arr a b] -> arr [a] [b]
\end{lstlisting}
Sometimes parallel Haskells require additional configuration parameters as information about the execution environment. This is why we also introduce an additional \code{conf} parameter to the function. We also do not want \code{conf} to be a fixed type, as the configuration parameters can differ for different instances of \code{ArrowParallel}. So we add it to the type signature of the typeclass as well.
\begin{lstlisting}[frame=htrbl]
class Arrow arr => ArrowParallel arr a b conf where
	parEvalN :: conf -> [arr a b] -> arr [a] [b]
\end{lstlisting}
We don't require the conf parameter in every implementation. If it is not needed, we usually want to allow the \code{conf} type parameter to be of any type and don't even evaluate it by blanking it in the type signature of the implemented \code{parEvalN} as we will see in the implementation of the Multicore and the ParMonad backend.

\subsection{Multicore Haskell}
The Multicore Haskell implementation of this class is straightforward using listApp from chapter \ref{utilfns} combined with the \code{using} operator from Multicore Haskell.
\begin{lstlisting}[frame=htrbl]
instance (NFData b, ArrowApply arr, ArrowChoice arr) =>
	ArrowParallel arr a b conf where
		parEvalN _ fs = listApp fs >>> arr (flip using $ parList rdeepseq)
\end{lstlisting}
We hardcode the \code{parList rdeepseq} strategy here, as in this context it is the only one making sense, since we usually want the output list to be fully evaluated to its normal form.

\subsection{ParMonad}
The ParMonad implementation makes use of Haskells laziness and ParMonad's \code{spawnP :: NFData a => a -> Par (IVar a)} function, which forks away the computation of a value and returns an IVar containing the result in the Par monad.
\\\\
We therefore apply each function to its corresponding input value with \code{app} and then fork the computation away with \code{arr spawnP} inside a \code{zipWithArr} call. This yields a list \code{[Par (IVar b)]}, which we then convert into \code{Par [IVar b]} with \code{arr sequenceA}. In order to wait for the computation to finish, we map over the \code{IVar}s inside the ParMonad with \code{arr (>>= mapM get)}. The result of this operation is a \code{Par [b]} from which we can finally remove the monad again by running \code{arr runPar} to get our output of \code{[b]}.
\begin{lstlisting}[frame=htrbl]
instance (NFData b, ArrowApply arr, ArrowChoice arr) =>
	ArrowParallel arr a b conf where
		parEvalN _ fs = 
			(arr $ \as -> (fs, as)) >>>
			zipWithArr (app >>> arr spawnP) >>>
			arr sequenceA >>>
			arr (>>= mapM get) >>>
			arr runPar
\end{lstlisting}

\subsection{Eden}
For the Multicore and ParMonad implementation we could use general instances of \code{ArrowParallel} that just require the \code{ArrowApply} and \code{ArrowChoice} typeclasses. With Eden this is not the case as we can only spawn a list of functions and we cannot extract simple functions out of arrows. While we could still manage to have only one class in the module by introducing a typeclass like
\begin{lstlisting}[frame=htrbl]
class (Arrow arr) => ArrowUnwrap arr where
	arr a b -> (a -> b)
\end{lstlisting}
, we don't do it in this paper, as this seems too hacky. For now, we just implement \code{ArrowParallel} for normal functions
\begin{lstlisting}[frame=htrbl]
instance (Trans a, Trans b) => ArrowParallel (->) a b conf where
parEvalN _ fs as = spawnF fs as
\end{lstlisting}
and the Kleisli type.
\begin{lstlisting}[frame=htrbl]
instance (Monad m, Trans a, Trans b, Trans (m b)) =>
	ArrowParallel (Kleisli m) a b conf where
parEvalN conf fs =
	(arr $ parEvalN conf (map (\(Kleisli f) -> f) fs)) >>>
	(Kleisli $ sequence)
\end{lstlisting}

\subsection{Benefits of parallel Arrows}
We have seen that we can wrap parallel Haskells inside of the \code{ArrowParallel} interface, but why do we abstract parallelism this way and what does this approach do better than the other parallel Haskells?
\begin{itemize}
	\item \textbf{Arrow API benefits}:
	With the \code{ArrowParallel} typeclass we do not lose any benefits of using arrows as \code{parEvalN} is just yet another arrow combinator. The resulting arrow can be used in the same way its serial version can be used. This is a big advantage of this approach, especially compared to the monad solutions as all arrow combinators will continue to work instead of requiring special ones for each parallel monad.
	\item \textbf{Abstraction}:
	With the \code{ArrowParallel} typeclass, we abstracted all parallel implementation logic away from the business logic. This gives us the beautiful situation of being able to write our code against the interface the typeclass gives us without being bound to any parallel Haskell. So as an example, during development, we can run the code on the simple Multicore version and afterwards deploy it on a cluster by converting it into an Eden version, by just swapping out the actual \code{ArrowParallel} instance.
\end{itemize}

>>>>

\section{Parallel Arrows}
\subsection{The ArrowParallel typeclass}
\begin{lstlisting}[frame=htrbl]
parEvalN :: [a -> b] -> [a] -> [b]
\end{lstlisting}

\begin{lstlisting}[frame=htrbl]
parEvalN :: (Arrow arr) => [arr a b] -> arr [a] [b]
\end{lstlisting}

\frbreak

\begin{lstlisting}[frame=htrbl]
class Arrow arr => ArrowParallel arr a b where
	parEvalN :: [arr a b] -> arr [a] [b]
\end{lstlisting}
\begin{lstlisting}[frame=htrbl]
class Arrow arr => ArrowParallel arr a b conf where
	parEvalN :: conf -> [arr a b] -> arr [a] [b]
\end{lstlisting}

\frbreak

\subsection{Multicore Haskell}
\begin{lstlisting}[frame=htrbl]
instance (NFData b, ArrowApply arr, ArrowChoice arr) =>
	ArrowParallel arr a b conf where
		parEvalN _ fs = listApp fs >>> arr (flip using $ parList rdeepseq)
\end{lstlisting}

\frbreak
\subsection{ParMonad}
\begin{lstlisting}[frame=htrbl]
instance (NFData b, ArrowApply arr, ArrowChoice arr) =>
	ArrowParallel arr a b conf where
		parEvalN _ fs = 
			(arr $ \as -> (fs, as)) >>>
			zipWithArr (app >>> arr spawnP) >>>
			arr sequenceA >>>
			arr (>>= mapM get) >>>
			arr runPar
\end{lstlisting}

\frbreak
\subsection{Eden}
\begin{lstlisting}[frame=htrbl]
instance (Trans a, Trans b) => ArrowParallel (->) a b conf where
parEvalN _ fs as = spawnF fs as
\end{lstlisting}
and the Kleisli type.
\begin{lstlisting}[frame=htrbl]
instance (Monad m, Trans a, Trans b, Trans (m b)) =>
	ArrowParallel (Kleisli m) a b conf where
parEvalN conf fs =
	(arr $ parEvalN conf (map (\(Kleisli f) -> f) fs)) >>>
	(Kleisli $ sequence)
\end{lstlisting}

\begin{lstlisting}[frame=htrbl]
class (Arrow arr) => ArrowUnwrap arr where
arr a b -> (a -> b)
\end{lstlisting}

\frbreak

\subsection{Benefits of parallel Arrows}

### 2017-01-26 presentation/skeletons.tex
copied all the relevant content from the paper to the presentation

\subsection{parEvalNLazy}
\code{parEvalN} is 100\% strict, which means that it fully evaluates all passed arrows. Sometimes this might not be feasible, as it will not work on infinite lists of functions like e.g. \code{map (arr . (+)) [1..]} or just because we need the arrows evaluated in chunks. \code{parEvalNLazy} fixes this. It works by first chunking the input from \code{[a]} to \code{[[a]]} with the given \code{ChunkSize} in \code{(arr \$ chunksOf chunkSize)}. These chunks are then fed into a list \code{[arr [a] [b]]} of parallel arrows created by feeding chunks of the passed \code{ChunkSize} into the regular parEvalN by using \code{listApp}. The resulting \code{[[b]]} is lastly converted into \code{[b]} with \code{arr concat}.
\begin{lstlisting}[frame=htrbl]
parEvalNLazy :: (ArrowParallel arr a b conf, ArrowChoice arr, ArrowApply arr) =>
	conf -> ChunkSize -> [arr a b] -> (arr [a] [b])
parEvalNLazy conf chunkSize fs =
	arr (chunksOf chunkSize) >>>
	listApp fchunks >>>
	arr concat
	where
		fchunks = map (parEvalN conf) $ chunksOf chunkSize fs
\end{lstlisting}

\subsection{parEval2}
We have only talked about the paralellization arrows of the same type up until now. But sometimes we want to paralellize heterogenous types as well. For this, we introduce a helper combinator \code{arrMaybe} first, that converts an arrow \code{arr a b} to an arrow \code{arr (Maybe a) (Maybe b)}.
\begin{lstlisting}[frame=htrbl]
arrMaybe :: (ArrowApply arr) => (arr a b) -> arr (Maybe a) (Maybe b)
arrMaybe fn = (arr $ go) >>> app
	where 
		go Nothing = (arr $ \Nothing -> Nothing, Nothing)
		go (Just a) = ((arr $ \(Just x) -> (fn, x)) >>> app >>> arr Just, (Just a))
\end{lstlisting}
With this, we can now easily write \code{parEval2} which combines two arrows \code{arr a b} and \code{arr c d} into a new parallel arrow \code{arr (a, c) (b, d)}. We start by converting both arrows with \code{arrMaybe}, combining them with \code{***} into a new arrow \code{arr (Maybe a, Maybe c) (Maybe b, Maybe d)}. This is then replicated twice and fed into parEvalN to get a \code{arr [(Maybe a, Maybe c)] [(Maybe b, Maybe d)]}. We can then apply this arrow to the input \code{[(Just a, Nothing), (Nothing, Just c)]} and then extract the resulting values with \code{fromJust} and the \code{!!} operator on lists in the last step.
\begin{lstlisting}[frame=htrbl]
parEval2 :: (ArrowParallel arr a b conf,
	ArrowParallel arr (Maybe a, Maybe c) (Maybe b, Maybe d) conf,
	ArrowApply arr) =>
	conf -> arr a b -> arr c d -> (arr (a, c) (b, d))
parEval2 conf f g =
	(arr $ \(a, c) -> (f_g, [(Just a, Nothing), (Nothing, Just c)])) >>>
	app >>>
	(arr $ \comb -> (fromJust (fst (comb !! 0)), fromJust (snd (comb !! 1))))
where
	f_g = parEvalN conf $ replicate 2 $ arrMaybe f *** arrMaybe g
\end{lstlisting}

\subsection{parMap}
\code{parMap} is probably the most common skeleton for parallel programs. We can implement it with \code{ArrowParallel} by repeating an arrow \code{arr a b} and then passing it into \code{parEvalN} to get an arrow \code{arr [a] [b]}. 
Just like \code{parEvalN}, \code{parMap} is 100 \% strict.
\begin{lstlisting}[frame=htrbl]
parMap :: (ArrowParallel arr a b conf, ArrowApply arr) =>
	conf -> (arr a b) -> (arr [a] [b])
parMap conf f =
	(arr $ \as -> (f, as)) >>>
	(first $ arr repeat >>>
		arr (parEvalN conf)) >>>
	app
\end{lstlisting}

\subsection{parMapStream}
As \code{parMap} is 100\% strict it has the same restrictions as \code{parEvalN} compared to \code{parEvalNLazy}. So it makes sense to also have a \code{parMapStream} which behaves like \code{parMap}, but uses \code{parEvalNLazy} instead of \code{parEvalN}.
\begin{lstlisting}[frame=htrbl]
parMapStream :: (ArrowParallel arr a b conf, ArrowChoice arr, ArrowApply arr) =>
	conf -> ChunkSize -> arr a b -> arr [a] [b]
parMapStream conf chunkSize f =
	(arr $ \as -> (f, as)) >>>
	(first $ arr repeat >>>
		arr (parEvalNLazy conf chunkSize)) >>>
	app
\end{lstlisting}

\subsection{farm}
\code{parMap} spawns every single computation in a new thread (at least for the instances of \code{ArrowParallel} we gave in this paper). This can be quite wasteful and a \code{farm} that equally distributes the workload over \code{numCores} workers (if numCores is greater than actualProcessorCount, the fastest processor(s) to finish will get more tasks) seems useful.
\begin{lstlisting}[frame=htrbl]
farm :: (ArrowParallel arr a b conf, ArrowParallel arr [a] [b] conf,
	ArrowChoice arr, ArrowApply arr) =>
	conf -> NumCores -> arr a b -> arr [a] [b]
farm conf numCores f =
	(arr $ \as -> (f, as)) >>>
	(first $ arr mapArr >>> arr repeat >>>
		arr (parEvalN conf)) >>>
	(second $ arr (unshuffle numCores)) >>>
	app >>>
	arr shuffle
\end{lstlisting}
The definition of \code{unshuffle} is
\begin{lstlisting}[frame=htrbl]
unshuffle :: Int
	-> [a]
	-> [[a]]
unshuffle n xs = [takeEach n (drop i xs) | i <- [0..n-1]]
\end{lstlisting}
, while \code{shuffle} is defined as:
\begin{lstlisting}[frame=htrbl]
shuffle :: [[a]]
	-> [a]
shuffle = concat . transpose
\end{lstlisting}
(These were taken from Eden's source code. \cite{eden_skel_shuffle})

\subsection{farmChunk}
As \code{farm} is basically just \code{parMap} with a different work distribution, it is, again, 100\% strict. So we define \code{farmChunk} which uses \code{parEvalNLazy} instead of \code{parEvalN} like this:
\begin{lstlisting}[frame=htrbl]
farmChunk :: (ArrowParallel arr a b conf, ArrowParallel arr [a] [b] conf,
	ArrowChoice arr, ArrowApply arr) =>
	conf -> ChunkSize -> NumCores -> arr a b -> arr [a] [b]
farmChunk conf chunkSize numCores f =
	(arr $ \as -> (f, as)) >>>
	(first $ arr mapArr >>> arr repeat >>>
		arr (parEvalNLazy conf chunkSize)) >>>
	(second $ arr (unshuffle numCores)) >>>
	app >>>
	arr shuffle
\end{lstlisting}

>>>>

\subsection{parEvalNLazy}
\begin{lstlisting}[frame=htrbl]
parEvalNLazy :: (ArrowParallel arr a b conf, ArrowChoice arr, ArrowApply arr) =>
	conf -> ChunkSize -> [arr a b] -> (arr [a] [b])
parEvalNLazy conf chunkSize fs =
	arr (chunksOf chunkSize) >>>
	listApp fchunks >>>
	arr concat
	where
		fchunks = map (parEvalN conf) $ chunksOf chunkSize fs
\end{lstlisting}
\frbreak

\subsection{parEval2}
\begin{lstlisting}[frame=htrbl]
arrMaybe :: (ArrowApply arr) => (arr a b) -> arr (Maybe a) (Maybe b)
arrMaybe fn = (arr $ go) >>> app
	where 
		go Nothing = (arr $ \Nothing -> Nothing, Nothing)
		go (Just a) = ((arr $ \(Just x) -> (fn, x)) >>> app >>> arr Just, (Just a))
\end{lstlisting}
\frbreak

\begin{lstlisting}[frame=htrbl]
parEval2 :: (ArrowParallel arr a b conf,
	ArrowParallel arr (Maybe a, Maybe c) (Maybe b, Maybe d) conf,
	ArrowApply arr) =>
	conf -> arr a b -> arr c d -> (arr (a, c) (b, d))
parEval2 conf f g =
	(arr $ \(a, c) -> (f_g, [(Just a, Nothing), (Nothing, Just c)])) >>>
	app >>>
	(arr $ \comb -> (fromJust (fst (comb !! 0)), fromJust (snd (comb !! 1))))
where
	f_g = parEvalN conf $ replicate 2 $ arrMaybe f *** arrMaybe g
\end{lstlisting}

\frbreak
\subsection{parMap}
\begin{lstlisting}[frame=htrbl]
parMap :: (ArrowParallel arr a b conf, ArrowApply arr) =>
	conf -> (arr a b) -> (arr [a] [b])
parMap conf f =
	(arr $ \as -> (f, as)) >>>
	(first $ arr repeat >>>
		arr (parEvalN conf)) >>>
	app
\end{lstlisting}

\frbreak

\subsection{parMapStream}
\begin{lstlisting}[frame=htrbl]
parMapStream :: (ArrowParallel arr a b conf, ArrowChoice arr, ArrowApply arr) =>
	conf -> ChunkSize -> arr a b -> arr [a] [b]
parMapStream conf chunkSize f =
	(arr $ \as -> (f, as)) >>>
	(first $ arr repeat >>>
		arr (parEvalNLazy conf chunkSize)) >>>
	app
\end{lstlisting}

\frbreak
\subsection{farm}
\begin{lstlisting}[frame=htrbl]
farm :: (ArrowParallel arr a b conf, ArrowParallel arr [a] [b] conf,
	ArrowChoice arr, ArrowApply arr) =>
	conf -> NumCores -> arr a b -> arr [a] [b]
farm conf numCores f =
	(arr $ \as -> (f, as)) >>>
	(first $ arr mapArr >>> arr repeat >>>
		arr (parEvalN conf)) >>>
	(second $ arr (unshuffle numCores)) >>>
	app >>>
	arr shuffle
\end{lstlisting}
The definition of \code{unshuffle} is
\begin{lstlisting}[frame=htrbl]
unshuffle :: Int
	-> [a]
	-> [[a]]
unshuffle n xs = [takeEach n (drop i xs) | i <- [0..n-1]]
\end{lstlisting}
, while \code{shuffle} is defined as:
\begin{lstlisting}[frame=htrbl]
shuffle :: [[a]]
	-> [a]
shuffle = concat . transpose
\end{lstlisting}
(These were taken from Eden's source code. \cite{eden_skel_shuffle})

\frbreak

\subsection{farmChunk}
\begin{lstlisting}[frame=htrbl]
farmChunk :: (ArrowParallel arr a b conf, ArrowParallel arr [a] [b] conf,
	ArrowChoice arr, ArrowApply arr) =>
	conf -> ChunkSize -> NumCores -> arr a b -> arr [a] [b]
farmChunk conf chunkSize numCores f =
	(arr $ \as -> (f, as)) >>>
	(first $ arr mapArr >>> arr repeat >>>
		arr (parEvalNLazy conf chunkSize)) >>>
	(second $ arr (unshuffle numCores)) >>>
	app >>>
	arr shuffle
\end{lstlisting}
